\textbf{Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated}

### 2022-09-14 submission/manuscript.Rmd
Update manuscript.Rmd

<!-- stakes and Post-truth era -->
For the first time in the history of humanity, technology has enabled the creation of near-perfect simulations  indistinguishable from reality. These artificial yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality, artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access [@nightingale2022]. Such progress not only carries important consequences for the technological and entertainment sectors, but also for security and politics, for instance if used for propaganda and  disinformation, recruitment into malevolent organizations, or religious indoctrination [@pantserev2020]. This challenge is  thus central to what has been coined the "post-truth era" [@lewandowsky2017beyond], in which the distinction (and lack  thereof) between authentic and simulated objects will play a critical role.

<!-- Ambiguous stimuli and irrelevance of objective features -->
While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain  key details and an overall appearance of reality), it is fair to assume that these technical limitations will become  negligible in the near future. In fact, in the field of face perception and recognition, recent research found images of  artificially-generated faces to be perceived as more real than real faces [@nightingale2022; @tucciarelli2020; @moshel2022]. This fact, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective  characteristics (for instance, facial features in the perception of real relative to fake faces; [@holmes2016; @moshel2022]), how can we make judgments regarding their nature?

<!-- Context -->
Literature shows that the context surrounding a stimulus often plays an important  role in the assessment of its reality (a process henceforth referred to as *simulation monitoring* [@makowski2019phenomenal; @makowski2018cognitive]). Whereas individuals could rely on the content of the stimulus, making a reality judgement based solely on this information could be too cognitively effortful, especially if the stimulus is imbued with ambiguity [@michael2021source; @susmann2021persuasion]. As such, the Elaboration Likelihood Model(ELM) posits that people tend to draw on peripheral contextual cues, such as the source of the stimulus, credibility, authority and expertise of the source etc., to help facilitate their evaluation [petty1986elaboration]. Accordingly, such reliance on peripheral cues has been consistently reported across multiple studies, most recently with regards to people's trust in news articles reporting on the COVID-19 pandemic [@susmann2021persuasion;@michael2021source]. In the absence of these contextual information, however, what then  drives our beliefs of reality? (**Figure 1**).

>>>>

<!-- stakes and Post-truth era -->
For the first time in the history of humanity, technology has enabled the creation of near-perfect simulations  indistinguishable from reality. These artificial yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality, artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access [@nightingale2022]. Such progress not only carries important consequences for the technological and entertainment sectors, but also for security and politics, for instance if used for propaganda and  disinformation, recruitment into malevolent organizations, or religious indoctrination [@pantserev2020]. This issue is central to what has been coined the "post-truth era" [@lewandowsky2017beyond], in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.

<!-- Ambiguous stimuli and irrelevance of objective features -->
While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images), it is fair to assume that these technical limitations will become negligible in the near future, in  particular in the field of faces generation and replacement [@nightingale2022; @tucciarelli2020; @moshel2022]. This fact, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?

<!-- Context -->
Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality [a process henceforth referred to as *simulation monitoring*, @makowski2019phenomenal; @makowski2018cognitive]. The extensive search and processing of cues within ambiguous stimuli being and cognitively effortful [@michael2021source; @susmann2021persuasion]. 
Whereas individuals could rely on the content of the stimulus, making a reality judgement based solely on this information could be too cognitively effortful, especially if the stimulus is imbued with ambiguity [@michael2021source; @susmann2021persuasion]. As such, the Elaboration Likelihood Model (ELM) posits that people tend to draw on peripheral contextual cues, such as the source of the stimulus, credibility, authority and expertise of the source etc., to help facilitate their evaluation [petty1986elaboration]. Accordingly, such reliance on peripheral cues has been consistently reported across multiple studies, most recently with regards to people's trust in news articles reporting on the COVID-19 pandemic [@susmann2021persuasion;@michael2021source]. In the absence of these contextual information, however, what then  drives our beliefs of reality? (**Figure 1**).
